Linear response theory for core set identification

### 2012-07-19 writedown/linear.response/langevin.tex
fix bug
important improvement of the theory

\newcommand{\recheck}[1]{{\color{red} #1}}
\newcommand{\redc}[1]{{\color{red} #1}}
\newcommand{\bluec}[1]{{\color{blue} #1}}
\newcommand{\vect}[1]{\textbf{\textit{#1}}}
\newcommand{\dd}{\textsf{d}}

\newcommand{\mh}{\mathcal H}
\newcommand{\ml}{\mathcal L}
\newcommand{\mt}{\mathcal T}
\newcommand{\fwg}{{\mathcal A}}
\newcommand{\bwg}{{\mathcal B}}
\newcommand{\EX}{{\textrm{EX}}}
\newcommand{\CG}{{\textrm{CG}}}
\newcommand{\HY}{{\Delta}}
\newcommand{\bsigma}{\boldsymbol\sigma}

@@

  \dot{\vect q} & = \frac{\partial\mh}{\partial \vect p}

@@

  \dot{\vect p} & =- \frac{\partial\mh}{\partial \vect q}

@@

$F_e(t)$ is the strength of the perturbation as a function of time.

@@

@@

  \frac{\partial}{\partial t} f(\vect x, t) - \fwg f(\vect x, t) = 0
where $\fwg$ is the forward infiniesimal generator given by
  \fwg =

@@

  \frac{\partial \mh}{\partial\vect p} + \vect C F_e(t)

@@

  -\frac{\partial \mh}{\partial\vect q} +

@@

  + 3N\gamma

@@

@@

infiniesimal generator can be viewed as perturbation from the equilibrium
distribution (invariant measure) and the unperturbed operator

@@

respectively. We have
  f(\vect x, t) &= f_0(\vect x) + \Delta  f(\vect x, t)

@@

@@

  \fwg = \fwg_0 + \Delta\fwg(t)

@@

Where the invariant measure satisfies $\fwg_0f_0(\vect x) = 0$,

@@

  f_0(\vect x) \propto e^{-\beta\mh(\vect x)}

@@

The Kolmogorov forward equation for the perturbation is therefore

@@

  [f_0(\vect x) + \Delta  f(\vect x, t)]

@@

  [\,\fwg_0 + \Delta\fwg(t)\,]
  [\,f_0(\vect x) + \Delta  f(\vect x, t)\,] = 0

@@

The basic assumption for the ``linear response'' is that the high order
term $\Delta\fwg(t)  \Delta  f(\vect x, t)$ 
can be neglected. Noticing $\fwg_0 f_0(\vect x) = 0$, we have the
Kolmogorov forward equation
for the leading order of the perturbation:

@@

  - \fwg_0

@@

  \Delta  f(\vect x, t)

@@

  \Delta\fwg(t) f_0(\vect x)

@@

The operator on l.h.s. is the same as the unperturbed equation.
Formally solving this equation with initial condition
$\Delta f(\vect x, 0) = 0$ gives

@@

  \Delta  f(\vect x, t) =
  \int_0^t \dd s \:
  e^{(t-s)\fwg_0}
  \Delta\fwg(s)f_0(\vect x)

@@

By defining the \emph{dissipative flux},

@@

it has been shown that %~\cite{tuckeman2010statistical}

@@

  \Delta\fwg(s)f_0(\vect x) =
  -\beta f_0(\vect x)\, j(\vect x) F_e(s)

@@

For any observation:

@@

  [f_0(\vect x) + \Delta f(\vect x, t)] \\\nonumber

@@

  \langle O\rangle_0

@@

  e^{(t-s)\fwg_0}
  f_0(\vect x)\, j(\vect x)F_e(s)  \\\nonumber

@@

  e^{(t-s)\fwg_0}
  f_0(\vect x) j(\vect x)  \\\nonumber

@@

  f_0(\vect x) j(\vect x)\,
  e^{(t-s)\bwg_0}

@@

  f_0(\vect x) j(\vect x)\,
  e^{s\bwg_0}

@@

Where $\bwg_0$ is the infiniesimal generator of the \emph{unperturbed} 
Kolmogorov backward equation, which is the adjoint operator of $\fwg_0$.

@@

  e^{s\bwg_0} O(\vect x) = \mathbb E_{\vect x} [O(\vect X_s)]

@@

where $\vect X_t$ is the trajectory of the unperturbed Langevin equation

@@

  f_0(\vect x)

@@

  \mathbb E_{\vect x} [O(\vect X_s)]

@@

  \langle

@@

  \mathbb E_{\vect x} [O(\vect X_s)]
  \rangle_0

@@

  \mathbb E_{\vect x} [O(\vect X_s)]
  \rangle_0$ is the \emph{equilibrium time

@@

dissipative flux $j$ at time 0.

@@

measure $f_0$ under a propagator $\mt_\alpha$
of time step $\alpha$, which is associated with a
stochastic process denoted by $\vect Y_\alpha$:

@@

  C_\alpha = \big\{
  \vect x \,\vert\, \mt_\alpha f_0(\vect x) > f_0(\vect x)

@@

  \mathcal P f_0 (\vect y)

@@

  f_0(\vect x) \,

@@

  C_\alpha = \big\{

@@

  \mathcal P\mt_\alpha f_0(\vect y) > \mathcal P f_0(\vect y)

@@

For convenience, we define $\Delta \mt_\alpha =
\mt_\alpha - \mathcal I$, where $\mathcal I$ is the
identity. If $[\mathcal P\circ\Delta \mt_\alpha f_0](\vect y) > 0$, then
$\vect y$ is in the core set $\widetilde C_\alpha $.

@@

  [\mathcal P\circ\Delta \mt_\alpha f_0](\vect y)

@@

  \Delta \mt_\alpha f_0(\vect x) \,

@@

  \Delta \mt_\alpha f_0(\vect x) \,
  K_{\sigma} (\vect y - \vect y(\vect x))  \\\nonumber

@@

  \Delta \mt_\alpha f_0(\vect x) \,
  K_{\sigma, \vect y} (\vect x)  \\\nonumber
  f_0(\vect x) \,
  [\Delta \mt_\alpha]^\dagger K_{\sigma, \vect y} (\vect x)\\
  \lim_{\sigma \rightarrow 0}\,
  \langle
  [\Delta \mt_\alpha]^\dagger K_{\sigma, \vect y}
  \rangle_0

@@

where $[\Delta \mt_\alpha]^\dagger$ is the adjoint operator of $\Delta
\mt_\alpha$. The delta
function is replaced by the limit of a mollifier $K_\sigma(\vect y)$,
which is infinitely smooth, compact supported of size $\sigma$,
bounded and $\int
K_\sigma(\vect y)\dd \vect y = 1$.  The physical meaning is that we
can consider the expectation value of the stability of the mollifier
$K_{\sigma, \vect y}$ instead of the stability of the invariant measure.
This provides the convenience of using the linear response theory showed
in the previous section. By Eqn.~\eqref{eqn:lr},

@@

  [\mathcal P\circ\Delta \mt_\alpha f_t](\vect y)
  \lim_{\sigma \rightarrow 0}\,
  \langle
  [\Delta \mt_\alpha]^\dagger K_{\sigma, \vect y}
  \rangle_t \\\nonumber
  \lim_{\sigma \rightarrow 0}\,
  \langle
  [\Delta \mt_\alpha]^\dagger K_{\sigma, \vect y}
  \rangle_0  -

@@

  \langle
  \mathbb E_{\vect x}\{
  [\Delta \mt_\alpha]^\dagger K_{\sigma, \vect y}(\vect X_s)\,
  \}
  \rangle_0
  \Big\} \\ \label{eqn:main}

@@

  \lim_{\sigma \rightarrow 0}\,

@@

  \langle
  [\Delta \mt_\alpha]^\dagger K_{\sigma, \vect y}
  \rangle_0  -

@@

@@

  \mathbb E_{\vect x}
  \mathbb E_{\vect X_s}
  (K_{\sigma, \vect y}(\vect Y_\alpha))

@@

  K_{\sigma, \vect y}(\vect X_s)

@@

  \Big\rangle_0

@@

with initial conditions:
  \vect X_0 = \vect x; \quad \vect Y_0 = \vect X_s.
Therefore, the core set at time $t$ is defined by
  \widetilde C_\alpha^t =
  \vect y
  \,\Big\vert\,
  [\mathcal P\circ\Delta \mt_\alpha f_t](\vect y) > 0

\begin{figure}
  \centering
  \includegraphics[width=0.35\textwidth]{figs/fig-pot.eps}
  \caption{The potential with and without perturbation.}
  \label{fig:tmp1}
\end{figure}

@@

@@

>>>>

\newcommand{\recheck}[1]{{\color{red} #1}}
\newcommand{\redc}[1]{{\color{red} #1}}
\newcommand{\bluec}[1]{{\color{blue} #1}}
\newcommand{\vect}[1]{\textbf{\textit{#1}}}
\newcommand{\dd}{\textsf{d}}
\newcommand{\inv}{\textrm{inv}}

\newcommand{\mh}{\mathcal H}
\newcommand{\ml}{\mathcal L}
\newcommand{\mt}{\mathcal T}
\newcommand{\mo}{\mathcal O}
\newcommand{\mi}{\mathcal I}
\newcommand{\mc}{\mathcal C}
\newcommand{\fwg}{{\mathcal A}}
\newcommand{\bwg}{{\mathcal B}}
\newcommand{\bsigma}{\boldsymbol\sigma}

@@

  \dot{\vect q} & = \nabla_{\vect p}\mh(\vect q,\vect p)

@@

  \dot{\vect p} & =- \nabla_{\vect q}\mh(\vect q,\vect p)

@@

$F_e(t)$ is the strength of the perturbation as a function of time,
and is of order $\mo (\varepsilon)$, where $\varepsilon$ is assumed to be small.

@@

\begin{align}\label{eqn:orig-forward}
  \frac{\partial}{\partial t} f(\vect x, t) - \fwg^\beta(t) f(\vect x, t) = 0
where $\fwg^\beta(t)$ is the forward infiniesimal generator given by

@@

  \fwg^\beta(t) =

@@

  \nabla_{\vect p}\mh + \vect C F_e(t)

@@

  -\nabla_{\vect q}\mh +

@@

  + 3N\gamma,

@@

and $\beta$ is the inverse temperature.
The fluctuation-dissipation relation is always true:
$\beta = 2\gamma / \sigma^2$.

@@

infiniesimal generator can be viewed as perturbation from the initial
distribution and the unperturbed operator

@@

respectively. We the expansion with respect to small
variable $\varepsilon$:
\begin{align}\label{eqn:f-expan}
  f(\vect x, t) &= f_0(\vect x, t) + \varepsilon f_1(\vect x, t)
  +\varepsilon^2 f_2(\vect x, t) + \mo (\varepsilon^3),

@@

\begin{align}\label{eqn:A-expan}
  \fwg^\beta(t) = \fwg^\beta_0 + \varepsilon\fwg_1(t),
where

@@

  \fwg_0^\beta =&
  \nabla_{\vect p}\mh\cdot\nabla_{\vect q}
  - \big(
  -\nabla_{\vect q}\mh - \gamma\vect p
  \big)\cdot\nabla_{\vect p}
  + 3N\gamma,\\
  \fwg_1(t) =&
  - \frac{F_e(t)}{\varepsilon} \big(
  \vect C \cdot\nabla_{\vect q}
  \vect D \cdot\nabla_{\vect p}
  \big).

@@

Notice $F_e(t) \sim \mo(\varepsilon)$, so $\Vert\fwg_1(t)\Vert\sim\mo(1)$.
The invariant measure of $\fwg^\beta_0$ satisfies $\fwg^\beta_0f^\beta_{\inv}(\vect x) = 0$,

@@

  f^\beta_{\inv}(\vect x) \propto e^{-\beta\mh(\vect x)}

@@

Inserting \eqref{eqn:f-expan} and \eqref{eqn:A-expan} into
\eqref{eqn:orig-forward}, 
the Kolmogorov forward equation becomes:

@@

  [f_0(\vect x, t) + \varepsilon  f_1(\vect x, t) + \varepsilon^2f_2(\vect x, t)]

@@

  [\,\fwg^\beta_0 + \varepsilon\fwg_1(t)\,]
  [f_0(\vect x, t) + \varepsilon  f_1(\vect x, t) + \varepsilon^2f_2(\vect x, t)]
  = 0

@@

Matching this equation at different orders of $\varepsilon$, the zeroth
order gives:
\begin{align}\label{eqn:e-o0}

@@

  - \fwg_0^\beta

@@

  f_0(\vect x, t)
  = 0
which is the unperturbed equation. Matching the first and the second order gives:
\begin{align}\label{eqn:e-o1}
  - \fwg_0^\beta
  f_1(\vect x, t)
  =&
  \fwg_1(t) f_0(\vect x, t)\\\label{eqn:e-o2}
  - \fwg_0^\beta
  f_2(\vect x, t)
  =&
  \fwg_1(t) f_1(\vect x, t)
Formally solving \eqref{eqn:e-o0} -- \eqref{eqn:e-o2} with
inital conditions $f_1(\vect x, 0) = 0$ and $f_2(\vect x, 0) = 0$
gives
\begin{align}\label{eqn:f0-0}
  f_0(\vect x, t)
  e^{t\fwg^\beta_0}f_0(\vect x, 0) \\\label{eqn:f1-0}
  f_1(\vect x, t)
  e^{(t-s)\fwg^\beta_0}\circ
  \fwg_1(s) f_0(\vect x,s)

@@

  e^{(t-s)\fwg^\beta_0}\circ
  \fwg_1(s)\circ
  e^{s\fwg^\beta_0}f_0(\vect x, 0) \\\nonumber
  f_2(\vect x, t)
  e^{(t-s)\fwg^\beta_0}\circ
  \fwg_1(s) f_1(\vect x,s) \\\label{eqn:f2-0}
  \int_0^t\dd s
  \int_0^s\dd u\,\,
  e^{(t-s)\fwg^\beta_0}\circ
  \fwg_1(s)\circ
  e^{(s-u)\fwg^\beta_0}\circ
  \fwg_1(u)\circ
  e^{u\fwg^\beta_0}
  f_0(\vect x, 0) 

@@

If the initial distribution is the invariant distribution, i.e.
$f_0(\vect x, 0) = f_{\inv}^\beta(\vect x)$,
\eqref{eqn:f0-0} becomes:

@@

  f_0(\vect x, t) = f_{\inv}^\beta(\vect x)

@@

It can be shown that
  \fwg_1(s) f_{\inv}^\beta(\vect x)
  -\frac{F_e(s)}{\varepsilon}\beta
  j(\vect x)
  f_{\inv}^\beta(\vect x),
where the \emph{dissipative flux} $j(\vect x)$ is defined by,

@@

Then $f_1(\vect x, t)$ becomes:

@@

  f_1(\vect x, t)
  -\frac\beta\varepsilon
  F_e(s)\,
  e^{(t-s)\fwg^\beta_0}
  j(\vect x)
  f_{\inv}^\beta(\vect x)

@@

Therefore, the linear order approximation to
the solution of~\eqref{eqn:orig-forward} is 
\begin{align}\label{eqn:solv-orig-linear}
  f(\vect x, t) =
  f_{\inv}^\beta(\vect x)
  - \beta
  F_e(s)\,
  e^{(t-s)\fwg^\beta_0}
  j(\vect x)
  f_{\inv}^\beta(\vect x)
  + \mo(\varepsilon^2)
For any time-dependent observation, the linear response approximation
would be:

@@

  [\,f_{\inv}^\beta(\vect x) + \varepsilon f_1(\vect x, t)] \\\nonumber

@@

  \langle O\rangle

@@

  \int_0^t\dd s\,F_e(s)
  e^{(t-s)\fwg_0^\beta}
  \big[j(\vect x)f^\beta_{\inv}(\vect x)\big]
  \\\nonumber

@@

  e^{(t-s)\fwg_0^\beta}
  \big[j(\vect x)f^\beta_{\inv}(\vect x)\big]
  \\\nonumber

@@

  f^\beta_{\inv}(\vect x) j(\vect x)\,
  e^{(t-s)\bwg^\beta_0}

@@

  f^\beta_{\inv}(\vect x) j(\vect x)\,
  e^{s\bwg_0^\beta}

@@

Where $\bwg^\beta_0$ is the infiniesimal generator of the \emph{unperturbed} 
Kolmogorov backward equation, which is the adjoint operator of $\fwg^\beta_0$.

@@

  e^{s\bwg^\beta_0} O(\vect x) = \mathbb E_{\vect x} [O(\vect X^\beta_s)]

@@

where $\vect X^\beta_t$ is the trajectory of the unperturbed Langevin equation

@@

  f^\beta_{\inv}(\vect x)

@@

  \mathbb E_{\vect x} [O(\vect X^\beta_s)]

@@

@@

  \mathbb E_{\vect x} [O(\vect X^\beta_s)]
  \big\rangle

@@

  \mathbb E_{\vect x} [O(\vect X^\beta_s)]
  \rangle$ is the \emph{equilibrium time

@@

dissipative flux $j$.

@@

measure $f^\beta_{\inv}$ under a propagator $\mt_\tau$
of time step $\tau$.
For example, the propagator is chosen $\mt_\tau = e^{\tau\fwg_t^{2\beta}}$,
i.e. integrating the Langevin equation~\eqref{eqn:langevin-1}
and \eqref{eqn:langevin-2} at temperature $1/2\beta$ for time $\tau$.
Notice $\tau$ is an artificial time that is ``orthogonal'' to the real
time $t$.
% , which is associated with a
% stochastic process denoted by $\vect Y_\alpha$:
The core set is identified by:

@@

  C_\tau(t) = \big\{
  \vect x \,\vert\, \mt_\tau f(\vect x, t) > f(\vect x, t)

@@

  \mathcal P f (\vect y, t)

@@

  f(\vect x, t) \,

@@

  C_\tau(t) = \big\{

@@

  \mathcal P\mt_\tau f(\vect y, t) > \mathcal P f(\vect y, t)

@@

For convenience, we define $\Delta \mt_\tau =
\mt_\tau - \mathcal I$, where $\mathcal I$ is the
identity. If $[\mathcal P\circ\Delta \mt_\tau f](\vect y, t) > 0$, then
$\vect y$ is in the core set $\widetilde C_\tau(t) $.

@@

  [\mathcal P\circ\Delta \mt_\tau f](\vect y, t)

@@

  \Delta \mt_\tau f(\vect x, t) \,

@@

  \Delta \mt_\tau f(\vect x, t) \,
  K_{\sigma} (\vect y - \vect y(\vect x))  \\\label{eqn:core-identify}

@@

  \Delta \mt_\tau f(\vect x, t) \,
  K_{\sigma, \vect y} (\vect x)
  % \\\nonumber
  % &=
  % \lim_{\sigma \rightarrow 0}
  % f_0(\vect x) \,
  % [\Delta \mt_\alpha]^\dagger K_{\sigma, \vect y} (\vect x)\\
  % &=
  % \lim_{\sigma \rightarrow 0}\,
  % \langle
  % [\Delta \mt_\alpha]^\dagger K_{\sigma, \vect y}
  % \rangle_0

@@

For convenience, we denote $f_t(\vect x) = f(\vect x, t)$.
Notice that $\mt_\tau f_t(\vect x) = e^{\tau \fwg_t^{2\beta}} f_t(\vect x)$
is the solution of
  \frac{\partial}{\partial \tau} f_t(\vect x, \tau)
  \fwg^{2\beta}(t)  f_t(\vect x, \tau)
  =0
with inital condition $f_t(\vect x, \tau = 0) = f_t(\vect x)$. We do the same
expansion as before, and then
matching different orders of $\varepsilon$ gives:
  &\bigg[
  \frac{\partial}{\partial \tau}
  - \fwg_0^{2\beta}
  f_{t,0}(\vect x, \tau)
  = 0 \\
  &\bigg[
  \frac{\partial}{\partial \tau}
  - \fwg_0^{2\beta}
  f_{t,1}(\vect x, \tau)
  \fwg_1(t) f_{t,0}(\vect x, \tau)
Formally solving these equations with
inital conditions $f_{t,0}(\vect x, 0) = f_t(\vect x) = f(\vect x, t)$
and  $f_{t,1}(\vect x, 0) = 0$ 
gives
\begin{align}\label{eqn:f0-1}
  f_{t,0}(\vect x, \tau)
  e^{\tau\fwg^{2\beta}_0}f_{t,0}(\vect x, 0) \\\label{eqn:f1-1}
  f_{t,1}(\vect x, \tau)
  \int_0^\tau\dd \eta\,
  e^{(\tau-\eta)\fwg^{2\beta}_0}\circ
  \fwg_1(t) f_{t,0}(\vect x,\eta)
  \int_0^\tau\dd \eta\,
  e^{(\tau-\eta)\fwg^{2\beta}_0}\circ
  \fwg_1(t)\circ
  e^{\eta\fwg^{2\beta}_0}f_{t,0}(\vect x, 0) 
By inserting the linear order approximated solution~\eqref{eqn:solv-orig-linear}
in to the above equations, we have:

@@

  \mt_\tau f_t(\vect x)=
  f_{t}(\vect x, \tau)
  e^{\tau\fwg^{2\beta}_0} f_{\inv}^\beta(\vect x) -

@@

  F_e(s)\,
  e^{\tau\fwg^{2\beta}_0} \circ
  e^{(t-s)\fwg^\beta_0}
  j(\vect x)
  f_{\inv}^\beta(\vect x)
  \\\label{eqn:solve-tau-linear}
  &\,+ \varepsilon
  \int_0^\tau\dd \eta\,
  e^{(\tau-\eta)\fwg^{2\beta}_0}\circ
  \fwg_1(t)\circ
  e^{\eta\fwg^{2\beta}_0}f_{\inv}^\beta(\vect x)  + \mo(\varepsilon^2)
By inserting~\eqref{eqn:solv-orig-linear} and~\eqref{eqn:solve-tau-linear}
into~\eqref{eqn:core-identify}, we have, up to the first order
approximation,
  [\mathcal P\circ\Delta\mt_\tau f](\vect y, t)
  \approx
  \bigg\{
    &\,
    \big(e^{\tau\fwg_0^{2\beta}}-\mi\big)
    f_{\inv}^\beta(\vect x)\,
    K_{\sigma,\vect y}(\vect x)\\\nonumber
    - \int_0^t\dd s\,
    \int\dd \vect x\,
    \big(e^{\tau\fwg^{2\beta}_0} - \mi\big)\circ
    e^{(t-s)\fwg^\beta_0}
    j(\vect x)
    f_{\inv}^\beta(\vect x)
    \big]\, K_{\sigma,\vect y}(\vect x) \\\nonumber
    \varepsilon
    \int_0^\tau\dd \eta
    \int\dd \vect x\,
    e^{(\tau-\eta)\fwg^{2\beta}_0}\circ
    \fwg_1(t)\circ
    e^{\eta\fwg^{2\beta}_0}f_{\inv}^\beta(\vect x)\,K_{\sigma,\vect y}(\vect x)
    \bigg\}     \\\nonumber
  \approx
  \bigg\{
  &\,
    \mathbb E_{\vect x}[ K_{\sigma,\vect y}(\vect X^{2\beta}_\tau) ]
    - K_{\sigma,\vect y}(\vect x)
    \Big\rangle\\\nonumber
    - \int_0^t\dd s\,
    \mathbb E_{\vect x}\big\{
    \mathbb E_{\vect X_{t-s}^\beta}[
    K_{\sigma,\vect y}(\vect X_\tau^{2\beta})
    ]
    K_{\sigma,\vect y}(\vect X_{t-s}^\beta)
    \Big\rangle\\\label{eqn:core-identify-approx-1}
    \varepsilon
    \int_0^\tau\dd \eta
    \int\dd \vect x\,
    e^{(\tau-\eta)\fwg^{2\beta}_0}\circ
    \fwg_1(t)\circ
    e^{\eta\fwg^{2\beta}_0}f_{\inv}^\beta(\vect x)\,K_{\sigma,\vect y}(\vect x)
    \bigg\}     
Unfortunately the last term on the r.h.s. of~\eqref{eqn:core-identify-approx-1}
is not easy to calculate. We will deal with it with
the path integral method introduced later.

To be more general, we study the two perturbed Langevin dynamics
(i.e. Eqn.~\eqref{eqn:langevin-1} and \eqref{eqn:langevin-2}) with
different perturbations that are given by $F_e^1(t)$ and $F_e^2(t)$,
respectively. 
By writing Eqn.~\eqref{eqn:langevin-1} and \eqref{eqn:langevin-2} as
\begin{align}
  \frac{\dd }{\dd t}
  \left[
    \begin{array}{l}
      \vect q\\
      \vect p
    \end{array}
  \right]
  =
  \left[
    \begin{array}{l}
      \nabla_{\vect p}\mh\\
      -\nabla_{\vect q}\mh - \gamma\vect p + F_e\vect D
    \end{array}
  \right]
  \dd t
  +
  \left[
    \begin{array}{cc}
      \epsilon \vect I & 0\\
      0 & \sigma\vect I
    \end{array}
  \right]
  \cdot
  \left[
    \begin{array}{l}
      \dd\vect W_t\\
      \dd\vect W_t
    \end{array}
  \right]
\end{align}
Using Girsanov's formula, to the leading order of $\Delta F_e = F_e^2 - F_e^1$,
we have
\begin{align}\label{eqn:girsanov-1}
  \frac{\dd\mathcal P^2[\vect X_t]}{\dd\mathcal P^1[\vect X_t]}
  &=
  \exp
  \Big\{
  \frac 1 {\sigma^2}
  \int_0^t
  [\dot{\vect p}_s +
  \gamma\vect p_s +
  \nabla_{\vect q}\mh(\vect q_s,\vect p_s)
  - F_e^1(s) \vect D(\vect q_s,\vect p_s)
  ]\cdot
  \vect D(\vect q_s,\vect p_s)
  \Delta F_e(s)\,
  \dd s
  + \mathcal O(\Delta F_e^2)
  \Big\} 
\end{align}

\subsection{Linear response theory of the core set identification,
  revisited by the path integral method}
For some observable $O[\vect X_\eta]$, which is a functional of the
stochastic process $\vect X_\eta$,
the trajectory ensemble average yields:
  \mo(t)
  \int \dd \mu_t(\vect x)
  \int_{\mc\{\vect x,0;\tau\}}
  O[\vect X_\eta]\,
  \dd \mathcal P^{2\beta}_t[\vect X_\eta],
where $\mu_t(\vect x)$
is the measure of the initial position, and obviously, we have
$\dd \mu_t(\vect x) = f_t(\vect x)\,\dd \vect x$.
The trajectory $\vect X_\eta \in {\mc\{\vect x,0;\tau\}}$, where
${\mc\{\vect x,0;\tau\}}$ denotes the set of all continuous but not
differentiable trajectories starting at $\vect x$ at artificial
time 0, and ending
at artificial time $\tau$.
$\mathcal P^{2\beta}_t$ denotes the measure of trajectories
developped under temperature $1/2\beta$
at real time $t$.
Since the perturbation is a function of time, this
measure also depends on time. The reference artificial dynamics is chosen
at $t=0$.
In this case, \eqref{eqn:girsanov-1} rewrites:
  \frac{\dd \mathcal P^{2\beta}_t[\vect X_\eta]}
  {\dd \mathcal P^{2\beta}_0[\vect X_\eta]}\,

@@

@@

  \int_0^\tau
  [\dot{\vect p}_\eta +
  \gamma\vect p_\eta +
  \nabla_{\vect q}\mh(\vect q_\eta,\vect p_\eta)
  \vect D(\vect q_\eta,\vect p_\eta)
  F_e(t)\,
  \dd \eta
  + \mathcal O(\varepsilon^2)
  \Big\}\\
  1+
  F_e(t)\,
  \int_0^\tau
  [\dot{\vect p}_\eta +
  \gamma\vect p_\eta +
  \nabla_{\vect q}\mh(\vect q_\eta,\vect p_\eta)
  \vect D(\vect q_\eta,\vect p_\eta)\,
  \dd \eta
  + \mathcal O(\varepsilon^2)  
Notice that $F_e(t)\sim \mo(\varepsilon)$.
For convenience, we denote
  G[\vect X_\eta] =
  \int_0^\tau
  [\dot{\vect p}_\eta +
  \gamma\vect p_\eta +
  \nabla_{\vect q}\mh(\vect q_\eta,\vect p_\eta)
  \vect D(\vect q_\eta,\vect p_\eta)\,
  \dd \eta
  \mo(t)
  \int \dd \vect x
  f(\vect x, t)
  \int_{\mc\{\vect x,0;\tau\}}
  O[\vect X_\eta]\,
  \frac{\dd \mathcal P^{2\beta}_t[\vect X_\eta]}
  {\dd \mathcal P^{2\beta}_0[\vect X_\eta]}\,
  \dd \mathcal P^{2\beta}_0[\vect X_\eta]  \\\nonumber
  \int \dd \vect x
  f_{0}(\vect x, t)
  + \varepsilon f_{1}(\vect x, t)
  + \mo(\varepsilon^2)
  \int_{\mc\{\vect x,0;\tau\}}
  O[\vect X_\eta]\,
  1 
  + F_e(t) G[\vect X_\eta]
  + \mo(\varepsilon^2)
  \dd \mathcal P^{2\beta}_0[\vect X_\eta]
  \\\nonumber
  \int \dd \vect x
  f_{0}(\vect x, t)
  \int_{\mc\{\vect x,0;\tau\}}
  O[\vect X_\eta]\,
  \dd \mathcal P^{2\beta}_0[\vect X_\eta]
  \varepsilon
  f_{1}(\vect x, t)
  \int_{\mc\{\vect x,0;\tau\}}
  O[\vect X_\eta]\,
  \dd \mathcal P^{2\beta}_0[\vect X_\eta]\\\label{eqn:solve-tau-linear-2-0}
  &+
  F_e(t)
  f_{0}(\vect x, t)
  \int_{\mc\{\vect x,0;\tau\}}
  O[\vect X_\eta]\,
  G[\vect X_\eta]\,
  \dd \mathcal P^{2\beta}_0[\vect X_\eta]
  + \mo(\varepsilon^2) 
In the case of core set identification,
  [\mathcal P\circ \mt_\tau] f(\vect y,t)
  \int\dd \vect x\,
  \mt_\tau f(\vect x,t) K_{\sigma,\vect y}(\vect x)\\\nonumber
  \int\dd \vect x\,
  e^{\tau\fwg_t^{2\beta}} f(\vect x,t) \,K_{\sigma,\vect y}(\vect x)\\\nonumber
  \int\dd \vect x\,
  f(\vect x,t) \,e^{\tau\bwg_t^{2\beta}}K_{\sigma,\vect y}(\vect x)  \\\nonumber
  \int\dd \vect x\,
  f(\vect x,t) \,\mathbb E_{\vect x}
  K_{\sigma,\vect y}(\vect X^{2\beta}_{t,\tau})
  \\
  \int\dd \vect x\,
  f(\vect x,t) 
  \int_{\mc\{\vect x,0;\tau\}} K_{\sigma,\vect y}(\vect X_\eta)\,
  \dd\mathcal P^{2\beta}_t[\vect X_\eta]
So the observable $O[\vect X_\eta]$
is:
  O[\vect X_\eta] = 
  K_{\sigma,\vect y}(\vect X_\tau),
  % -
  % K_{\sigma,\vect y}(\vect x)
which is the end point of the artificial
trajectory measured by $K_{\sigma,\vect y}$.
Inserting everything we known in~\eqref{eqn:solve-tau-linear-2-0},
and notice $G[\vect X_\eta] = 0$ when $\tau = 0$,
  [\mathcal P\circ\Delta\mt_\tau f](\vect y, t)
  \big\{
  &\,
  [\mathcal P\circ\mt_\tau f - \mathcal P\circ\mt_0 f](\vect y, t)
  \big\}\\\nonumber
  \approx
  \bigg\{
  &\,
  f_\inv^\beta(\vect x)
  \int_{\mc\{\vect x,0;\tau\}}
  [K_{\sigma,\vect y}(\vect X_\tau)
  -K_{\sigma,\vect y}(\vect x)]  \,
  \dd \mathcal P^{2\beta}_0[\vect X_\eta]\\\nonumber

@@

  \int_0^t\dd s\, F_e(s)
  e^{(t-s)\fwg_0^\beta}
  j(\vect x)
  f_\inv^\beta(\vect x)
  \int_{\mc\{\vect x,0;\tau\}}
  [K_{\sigma,\vect y}(\vect X_\tau)
  -K_{\sigma,\vect y}(\vect x)]  \,
  \dd \mathcal P^{2\beta}_0[\vect X_\eta]\\\nonumber
  &\,+
  F_e(t)
  f_\inv^\beta(\vect x)
  \int_{\mc\{\vect x,0;\tau\}}
  K_{\sigma,\vect y}(\vect X_\tau)
  % \Big\{
  % \int_0^\tau\dd \eta\,
  % [\dot{\vect p}_\eta + \gamma\vect p_\eta + \nabla_{\vect q}\mh(\vect X_\eta)]
  % \cdot\vect D(\vect X_\eta)
  % \Big\}\,
  \,G[\vect X_\eta]\,
  \dd \mathcal P^{2\beta}_0[\vect X_\eta]
  \bigg\}\\\nonumber
  \approx
  \bigg\{
  &\,

@@

  \mathbb E_{\vect x}[K_{\sigma,\vect y}(\vect X_\tau^{2\beta})]

@@

  K_{\sigma,\vect y}(\vect x)
  \Big\rangle\\\nonumber
  &\,
  - \beta
  \int_0^t\dd s\, F_e(s)
  j(\vect x)
  \mathbb E_{\vect x} \big\{
  \mathbb E_{\vect X^\beta_{t-s}}\big[
  K_{\sigma, \vect y}(\vect X^{2\beta}_\tau)

@@

  K_{\sigma, y}(\vect X^\beta_{t-s})
  \Big\rangle\\\label{eqn:core-identify-approx-2}
  &\,+
  F_e(t)
  f_\inv^\beta(\vect x)
  \int_{\mc\{\vect x,0;\tau\}}
  K_{\sigma,\vect y}(\vect X_\tau)
  \,G[\vect X_\eta]\,
  \dd \mathcal P^{2\beta}_0[\vect X_\eta]
  \bigg\}

@@

Comparing~\eqref{eqn:core-identify-approx-2}
with~\eqref{eqn:core-identify-approx-1}, the first
two terms on the r.h.s. are identical. 
The last term is now computable.

@@

\begin{figure}
  \centering
  \includegraphics[width=0.4\textwidth]{figs/fig-pot.eps}
  \caption{The potential with and without perturbation.}
  \label{fig:tmp1}
\end{figure}

@@

  - F_e^1(s) \vect D(\vect q_s,\vect p_s)
